\section{Discussion}
\label{sec:discussion}

\textbf{Limitations.}
Cross-modality $\kappa$ on math175 is sensitive to small marginal
$\pi$ shifts and disappears in the very-low-$\pi$ regime
(\S\ref{sec:ablation_A4}). DAJV is a discrete aggregation rule
that ignores verifier-confidence signals; a continuous-score
extension is planned. Contamination-clean splits (AIME, $n=30$;
CleanMath, $n=125$) are thin.

\textbf{Positioning.}
The Kuai joint-error bound and the
\citet{balasubramanian2026ising} Ising model subsume our
Theorem~\ref{thm:bound} as a special case; we make no claim of
priority on the abstract problem. The cross-modality independence
measurement is orthogonal to all three concurrent
2026 works~\citep{kuai2026independence,zhao2026care,balasubramanian2026ising}.
BSIA is the only one of five tested cross-modality aggregators
that produces a Pareto improvement on default DAJV (BSIA-iso:
$34\%$ ECE reduction at matched precision on math175; BSIA-fixed:
$+4.4$pp coverage at $0.962$ precision). Coverage gain below the
pre-registered $\geq 5$pp threshold. BSIA-iso also remains stable
where default DAJV breaks: on B-full at $k=12$ default precision
collapses to $0.42$ while BSIA-iso holds at $0.993$
(Appendix~\ref{app:k10_robustness}). Tightening coverage-side
exploitation (higher-order Bahadur expansion,
problem-conditional sparsity) remains open.

\textbf{Future work (pre-registered).}
Per \texttt{PRE\_REGISTRATION\_v2.md}: extractor-scaling beyond
$k=12$ (a second Meta extractor should close the H6 gap to
$\alpha = 0.05$); continuous-score extension; BSIA tightening to
the full $5$pp coverage criterion.

\textbf{Broader impact.}
DAJV supports \emph{abstention}, not commitment. Deploying in
high-stakes settings without a human-in-the-loop fallback would
invert the safety pattern; we recommend against this. BSD-3
license.
