\section{Empirical Results}
\label{sec:empirical}

\textbf{Setup.} A $k=12$ four-lab ensemble: 5 OpenAI (gpt-oss-120B,
gpt-5-mini, gpt-4o, gpt-4.1, gpt-5), 4 Anthropic (Claude Sonnet 4.6,
Opus 4.7, Opus 4.6, Haiku 4.5), 2 Alibaba (Qwen3-Coder-480B,
Qwen3-235B), 1 Meta (Llama-3.3-70B), evaluated on $n=330$ problems
spanning a MATH-175 subset, AIME 2025, and a CleanMath combo
(HMMT-Feb 2025, BRUMO 2025, SMT 2025, APEX 2025). Full ablations
(seed-stability, LOO extractor, solver rotation, calibration-size,
per-bench breakdowns) are in the appendix.

\subsection{Cross-modality independence}
\label{sec:cross_modality}

Each LLM $i$ contributes a structural vote $\sigma_i$ (script
classifies as ``working'') and an executable vote $\xi_i$ (script
accepts the candidate). Standard ``accept'' is
$\sigma_i \wedge \xi_i$. Table~\ref{tab:cross_modality} reports
median pairwise $\kappa$ on the wrong-candidate subset.

\begin{table}[h]
\centering
\caption{\textbf{Cross-modality independence (12-extractor
ensemble).} Wrong-candidate subset of math175 ($n_{\text{wrong}} = 47$)
and full Group B ($n_{\text{wrong}} = 192$). Within-modality
$\kappa$ is substantial; cross-LLM cross-modality $\kappa$ is two
orders of magnitude smaller on B-full.}
\label{tab:cross_modality}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lrrr}
\toprule
Bucket                         & math175 & B-full & $n$ pairs \\
\midrule
Within-modality, structural    & $0.545$ & $0.538$ &  66 \\
Within-modality, executable    & $0.777$ & $0.761$ &  66 \\
Within-LLM, cross-modality     & $0.112$ & $0.029$ &  12 \\
Cross-LLM, cross-modality      & $0.049$ & $\mathbf{0.009}$ & 132 \\
\bottomrule
\end{tabular}
\end{table}

The Python interpreter is an oracle, so cross-modality dependence
captures only how often two LLMs encode the same constraint into
Python and run it to the same verdict. Concurrent dependency-aware
aggregators~\citep{kuai2026independence,zhao2026care,balasubramanian2026ising}
collapse each LLM to a single signal and cannot exploit this
$k$-dimensional axis of independence.

\subsection{DAJV operating point}

Table~\ref{tab:aggregation} reports DAJV vs naive baselines on
math175 test split ($n_{\text{test}} = 53$, $n_{\text{cal}} = 122$).

\begin{table}[h]
\centering
\caption{\textbf{math175 test split, $k=8$ ensemble.} DAJV matches
naive unanimous precision while gaining $+13$pp coverage and
halving ECE.}
\label{tab:aggregation}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lrrrr}
\toprule
Method & Cov. & Prec. & ECE & Brier \\
\midrule
Naive unan.   & $.491$ & $.962$ & $.208$ & $.186$ \\
Naive maj.    & $.585$ & $.968$ & ---    & ---    \\
CARE-style    & $.358$ & $.421$ & $.575$ & $.693$ \\
\textbf{DAJV} & $\mathbf{.623}$ & $\mathbf{.970}$ & $\mathbf{.111}$ & $\mathbf{.143}$ \\
\bottomrule
\end{tabular}
\end{table}

DAJV reaches $32/33 = 0.97$ precision at $62\%$ coverage and reduces
ECE by $47\%$ vs naive unanimous. CARE collapses because the
calibration set has too few correct examples on contamination-clean
splits ($0$ on AIME, $5$ on CleanMath) for reliable logistic
fitting. Risk-coverage curves and contamination-clean numbers in
Appendix~\ref{app:extended}.

\subsection{BSIA partial pass of H7'}

Five cross-modality aggregators were pre-registered. The four
naive variants (factorised Bayes, agreement gate, per-LLM joint NB,
struct-gated exec-DAJV) all degrade default DAJV on at least one of
(cov, prec, ECE). BSIA is the only one that improves
(Table~\ref{tab:h7_brief}). BSIA-iso reduces ECE by $34\%$ at
matched precision; BSIA-fixed gains $+4.4$pp coverage at $0.962$
precision; BSIA-nested-CV gains $+3.8$pp coverage at $0.972$
precision -- below the $\geq 5$pp pre-registered threshold.

\begin{table}[h]
\centering
\caption{\textbf{BSIA suite, math175 $k=8$ (10 seeds).}}
\label{tab:h7_brief}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lrrr}
\toprule
Method & Cov. & Prec. & ECE \\
\midrule
default DAJV     & $.581$ & $.984$ & $.111$ \\
BSIA fixed       & $\mathbf{.625}$ & $.962$ & $.102$ \\
BSIA nested-CV   & $.619$ & $.972$ & $.086$ \\
\textbf{BSIA iso}& $.557$ & $.984$ & $\mathbf{.073}$ \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Robustness at $k=12$.} Default DAJV's copula MLE
overfits the $k(k-1)/2 = 66$ pairwise interactions when
$n_{\text{cal}} = 231$ B-full draws are below the
Theorem~\ref{thm:sample} threshold; precision collapses to $0.42$.
BSIA-iso holds at precision $0.993$, ECE $0.078$
(Appendix~\ref{app:k10_robustness}). Recommended deployment
variant for large $k$.

\subsection{H6: within-lab vs cross-lab dependency}

On B-full $k=12$ the within-lab median $\kappa = 0.664$ (17 pairs)
exceeds the cross-lab median $\kappa = 0.496$ (49 pairs). The
single-sided permutation test reaches $p = 0.091$ at $k=12$ (vs
$p = 0.32$ at $k=8$); adding Meta lab unlocked cross-lab diversity.
A second Meta extractor would close the remaining gap to
$\alpha = 0.05$.

\subsection{Cross-distribution validation}

On a 150-problem stratified ProcessBench-Math subset (3 OpenAI
extractors, gold-free mode), DAJV achieves $5\times$ commit
coverage ($5/22$ vs $1/22$) vs naive unanimous at matched
precision $1.000$ and matched specificity $1.000$, with ECE
$0.114$ vs $0.267$ ($57\%$ reduction).

\subsection{Pre-registered cross-benchmark transfer fails (Branch B)}
\label{sec:ablation_A4}

H4 ($|\Delta \kappa| \leq 0.10$ across $70\%$ of pairs) fails:
$0/6$ pairs satisfy it because near-zero accept rates on
contamination-clean splits make $\kappa$ degenerate. Branch B is
activated: DAJV must be re-fit per benchmark family.
