\section{Introduction}
\label{sec:introduction}

Selective prediction for LLMs on math reasoning frequently aggregates
accept/reject verdicts from multiple cross-family
verifiers~\citep{kuhn2023semantic,lightman2024prm,dtv2024,kim2025correlated}.
The independence assumption that underpins classical jury aggregation
is empirically false: \citet{kim2025correlated} report $60\%$
pairwise agreement on errors across 350+ LLMs;
\citet{kuai2026independence} document entanglement among 18 frontier
LLMs; \citet{denisovblanch2026consensus} report that LLM consensus
does not track truth even at $25\times$ sampling.

\textbf{Our pivot.} In math reasoning, each LLM emits a deterministic
Python verifier executed by an oracle. The Python execution is a
second modality of evidence, essentially independent of the LLM's
classification of its own emitted verifier (cross-modality
$\kappa \approx 0.009$ over $132$ cross-LLM pairs in a $k=12$
four-lab ensemble; within-modality $\kappa \approx 0.78$). Pure
LLM-jury aggregators~\citep{kuai2026independence,zhao2026care,balasubramanian2026ising}
collapse each LLM to a single signal and cannot exploit this axis.

\textbf{Contributions.}
(i) Cross-modality independence measurement on a $12$-extractor
four-lab ensemble (\S\ref{sec:cross_modality}, $132$ cross-LLM
pairs, $\kappa = 0.009$ on B-full).
(ii) Calibrated dependency-aware aggregation rule DAJV
(\S\ref{sec:method}) with a tight joint-FP
bound~(Theorem~\ref{thm:bound}, a specialization
of~\citet{balasubramanian2026ising} to binary votes) and a
sample-complexity bound~(Theorem~\ref{thm:sample}).
(iii) Block-Sparse Ising Aggregator (BSIA): per-LLM
$2 \!\times\! 2$ cells, within-modality cross-LLM Pearson
corrections, cross-LLM cross-modality interactions pinned to zero.
The only one of five tested cross-modality aggregators that
improves on default DAJV: BSIA-iso reduces ECE by $34\%$ at matched
precision; BSIA-fixed gains $+4.4$pp coverage at $0.962$
precision; partial pass of the pre-registered $\geq 5$pp coverage
criterion. Sample-complexity saving $k(k-2)$ parameters over
saturated Ising (Theorem~\ref{thm:bsia}).
(iv) Open-source library \texttt{verifyensemble} (BSD-3).
