\section{Method}
\label{sec:method}

\textbf{Setup.} A problem $x$ has gold answer $a$, a solver
produces candidate $\hat a$, and each verifier $E_i$ emits an
executable script that returns $V_i \in \{0, 1\}$ on $\hat a$. Let
$C := \mathbf{1}[\hat a = a]$. On the wrong-candidate distribution:
$\pi_i := \Pr[V_i = 1 \mid C = 0]$,
$\rho_{ij} := \mathrm{Corr}(V_i, V_j \mid C = 0)$.

\textbf{DAJV.} (i) \emph{Calibration:} on
$\mathcal{D}_{\text{cal}}$ of size $n_{\text{cal}}$, estimate
$\pi^{\pm}_i$ on the correct/wrong subsets,
$\rho^{\pm}_{ij}$, and prior $\pi_0$.
(ii) \emph{Deployment:} given vote vector $v$,
\begin{equation}
  \Pr[C = 1 \mid v] = \frac{\pi_0 \mathcal{L}^+(v)}{\pi_0 \mathcal{L}^+(v) + (1-\pi_0)\mathcal{L}^-(v)},
  \label{eq:posterior}
\end{equation}
where the second-order log-likelihood is
$\log \mathcal{L}^\pm(v) = \sum_i [v_i \log \pi^\pm_i +
(1{-}v_i)\log(1{-}\pi^\pm_i)] + \sum_{i<j} \rho^\pm_{ij}
(v_i - \pi^\pm_i)(v_j - \pi^\pm_j)$.
Recommend \textsc{Commit} if posterior $\geq \tau_{\text{c}} = 0.95$,
\textsc{Abstain} if $< 0.50$, else \textsc{Escalate}.

\textbf{BSIA.} Replaces the per-extractor binary vote $V_i$ with the
per-LLM $2 \!\times\! 2$ cell
$P_i(\sigma_i, \xi_i \mid C)$ on (structural, executable). Adds
within-modality cross-LLM Pearson corrections
$\rho^\sigma_{ij}, \rho^\xi_{ij}$ and pins cross-LLM cross-modality
interactions to zero (the empirical block-sparsity prior of
\S\ref{sec:cross_modality}). BSIA-iso applies a post-hoc
Pool-Adjacent-Violators isotonic recalibration on the
calibration-set posterior.

\textbf{Adversarial filter.} Before aggregation, each verifier is
probed against a gold-free perturbation set
$\mathcal{P}(\hat a) = \{\hat a \pm 1, \hat a + 7, 2\hat a\}$ for
integer $\hat a$. A verifier that accepts any probe contributes
\texttt{abstain} to the vote vector. Pattern
follows~\citep{dtv2024,bagheriNezhad2025symcode}; exact set locked
in pre-registration.
