\section{Related Work}
\label{sec:related}

\textbf{Selective prediction.}
Single-model confidence signals include
self-consistency~\citep{wang2023selfconsistency}, semantic
entropy~\citep{kuhn2023semantic,farquhar2024nature},
$p(\textsc{True})$~\citep{kadavath2022}, and process reward
models~\citep{lightman2024prm,qwenprm2025,skyworkprm2024}.
AbstentionBench~\citep{kirichenko2025abstentionbench} provides a
20-dataset benchmark.

\textbf{LLM-jury verification.}
Recent multi-LLM verifiers include
Math-Rev~\citep{liang2024mathrev}, ICE~\citep{omar2024ice},
SE-Jury~\citep{zhou2025sejury}, VERGE~\citep{singh2026verge}, and
LLM-PeerReview~\citep{chen2025peerreview}. Concurrent
dependency-aware aggregators
CARE~\citep{zhao2026care}, Kuai et al.~\citep{kuai2026independence},
and the Ising framework of~\citet{balasubramanian2026ising}
collapse each LLM to a single signal.

\textbf{Spec-grounded verification for math.}
DTV~\citep{dtv2024} introduces problem-grounded verification via
autoformalization to Isabelle. MATH-VF~\citep{kuoZhou2025mathvf}
combines a formalizer with an SMT critic.
SymCode~\citep{bagheriNezhad2025symcode} uses SymPy.
HERMES~\citep{ospanov2025hermes} interleaves informal reasoning
with Lean. DAJV adds a calibrated dependency-aware aggregation
layer on top of any executable spec-grounded verifier.

\textbf{Correlated errors.}
\citet{kim2025correlated} establish architecture-spanning
correlation; \citet{kuai2026independence} audit entanglement among
18 frontier LLMs; \citet{denisovblanch2026consensus} show
inference-time scaling fails to track truth.
\citet{lefort2024condorcet} reach the same conclusion via the
Condorcet jury theorem.

\textbf{Positioning.}
The Kuai joint-error bound and the
\citet{balasubramanian2026ising} Ising model subsume our
Theorem~\ref{thm:bound} as a special case. We make no claim of
priority on the abstract problem. The contribution we defend:
(i) the cross-modality independence measurement
(\S\ref{sec:cross_modality}); (ii) BSIA exploiting the empirically
observed sparsity prior; (iii) end-to-end empirical evaluation
with cross-distribution validation and a pre-registered protocol.

\textbf{Contamination.}
\citet{wu2025contam} show Qwen2.5-Math-7B reproduces $54.6\%$ of
MATH-500. MathArena~\citep{matharena2025} curates post-cutoff
problems for contamination-clean evaluation, which we use for the
held-out portion of our evaluation.
