%%%%%%%% ICML 2026 Workshop Submission - 4-page short paper format %%%%%%%
% Structure modeled on NeurIPS MATH-AI 2024 short papers and
% ICML AI4Math 2024 short-track papers (Abstract / Intro / Method /
% Results / Discussion in 4 pages, with unlimited refs and appendix).

\documentclass{article}

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\hypersetup{colorlinks=true, allcolors=black, pdfborder={0 0 0}}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,calc,shapes,fit,backgrounds}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{listings}
\lstdefinestyle{xsgrv}{
  basicstyle=\ttfamily\scriptsize\color{black},
  keywordstyle=\color{black},
  commentstyle=\color{black},
  stringstyle=\color{black},
  identifierstyle=\color{black},
  numbers=none,
  frame=single,
  framesep=3pt,
  framexleftmargin=2pt,
  framexrightmargin=2pt,
  rulecolor=\color{black},
  breaklines=true,
  breakatwhitespace=true,
  postbreak=\mbox{\textcolor{black}{$\hookrightarrow$}\space},
  showstringspaces=false,
  columns=fullflexible,
  keepspaces=true,
  xleftmargin=0pt,
  xrightmargin=0pt,
  linewidth=\linewidth,
  resetmargins=true,
  language=Python,
}

\usepackage{icml2026}
\icmltitlerunning{Cross-Family Symbolic Verification}

\begin{document}

\twocolumn[
\icmltitle{Supplementary Material for: \\
Cross-Family Symbolic Verification for \\
Contamination-Robust Selective Prediction on LLM Math Reasoning}

\begin{icmlauthorlist}
\icmlauthor{Anonymous Authors}{anon}
\end{icmlauthorlist}
\icmlaffiliation{anon}{Anonymous submission to an ICML 2026 workshop.}
\icmlcorrespondingauthor{Anonymous Authors}{anonymous@example.org}
\icmlkeywords{Selective Prediction, Math Reasoning, Verification, Contamination, LLM}

\vskip 0.3in
]

\printAffiliationsAndNotice{}

\onecolumn

\noindent\textbf{Note.} This document is the supplementary appendix accompanying the 4-page main paper. Section, table, figure, and listing numbering restart here.
\vspace{1em}

\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thetable}{\Alph{section}.\arabic{table}}
\renewcommand{\thefigure}{\Alph{section}.\arabic{figure}}
\setcounter{table}{0}
\setcounter{figure}{0}


The appendix supplements the 4-page main body with hyper-reproducible implementation
details, full statistical methodology, the pre-registration text, additional
results that did not fit in the main body, representative verifier
case studies, and a broader-impact discussion.

%------------------------------------------------------------------------------
\section{Extended Methods}
\label{app:methods}
%------------------------------------------------------------------------------

\subsection{Solver and extractor configuration}
\label{app:models}

The base solver is \texttt{Qwen2.5-7B-Instruct-Turbo} accessed via Together AI; for the false-acceptance analysis of self-verification the solver is the contamination-flagged \texttt{Qwen2.5-Math-7B-Instruct}~\citep{wu2025contam}. Solver sampling: $T{=}0$ greedy for the plurality candidate; $T{=}0.7$, top-$p$ $0.95$, $k{=}10$ for entropy and self-consistency baselines; \texttt{max\_tokens}{=}2048. The chain-of-thought prompt terminates with ``\texttt{The final answer is}~\$\textbackslash boxed\{\}\$.''.

Cross-family extractors: \texttt{Llama-3.3-70B-Instruct-Turbo}, \texttt{DeepSeek-V3}, \texttt{gpt-oss-120b}, \texttt{claude-sonnet-4-6}, \texttt{Qwen3-Coder-480B-A35B-Instruct}, \texttt{gpt-5-mini}. Extractor sampling: $T{=}0.2$, \texttt{max\_tokens}{=}2048, system prompt fixing the output format to a single Python code block. The frozen extractor prompt is in \Cref{lst:prompt}.

\begin{lstlisting}[style=xsgrv,caption={Frozen extractor prompt.},label={lst:prompt}]
You are a mathematics verification engineer. You will be shown a math problem.
Write a Python function

    def verify(answer) -> bool:

that returns True if `answer` (int, float, or sympy expression) satisfies the
problem's constraints, and False otherwise.

Hard rules:
  1. Do NOT solve the problem. Do NOT write `answer == <literal>`.
  2. Re-derive the problem's constraints from the statement and check that
     `answer` satisfies them.
  3. You may import sympy. itertools, math, fractions.Fraction, and
     collections.Counter are pre-imported.
  4. Wall-clock time < 10 seconds.
  5. If the problem requires a proof or has no bounded answer check, return
     EXACTLY the string `UNVERIFIABLE` and nothing else.
  6. Total script under 60 lines.

Problem: <<<PROBLEM>>>
\end{lstlisting}

\subsection{Sandbox and probe set}
\label{app:sandbox}

The emitted script is executed in a Python subprocess sandbox with a \texttt{SIGALRM} wall-clock timeout of 10 seconds. Exception trapping maps any \texttt{Exception} or \texttt{SystemExit} to a \texttt{False} return. The candidate $\hat a$ is cast through \texttt{sympify} before invocation; on \texttt{SympifyError} the candidate is passed as a string. Network sockets are not available in the subprocess.

The adversarial probe set $\mathcal P(\hat a) = \{\hat a-1, \hat a+1, \hat a+7, \hat a\times 2\}$ was selected on a 50-problem held-out development split of MATH-500 (strata-balanced, disjoint from any test set) and locked in the pre-registration. The four perturbations target trivial-True verifiers, additive-bias verifiers, modular-residue verifiers (the value $7$ is coprime with $\{2,3,4,5,6\}$), and multiplicative-scaling verifiers. For non-integer $\hat a$ the deterministic fallback set $\{0, 1, -1, 42, 100\} \setminus \{\hat a\}$ is used. A gold-relative variant of the same probe set is used only inside the benchmarking pipeline to compute the diagnostic Adv-FP column; the deployment-time filter never accesses the gold answer.

\subsection{PRM baselines}
\label{app:prm}

\texttt{Qwen2.5-Math-PRM-7B} and \texttt{Skywork-o1-Open-PRM-Qwen-2.5-7B} were run on Modal A100. For each problem and each of $10$ cached solver samples, per-step rewards were aggregated using min-step, mean-step, product-step, and last-step aggregations as documented on each model card; problem-level score is the max across the $10$ samples. PRMs were thresholded to match the X-SGRV top-tier coverage on each benchmark exactly. Skywork-PRM requires \texttt{torch\_dtype=torch.bfloat16}; on FP32 the model silently exhausts the A100's $40$\,GB of GPU memory for sequences longer than $\sim1{,}500$ tokens. The PRM scoring protocols were validated against published ProcessBench numbers on a 48-problem ProcessBench subset, reproducing the published values within 5 macro-F1 points on both PRMs.

\subsection{Verifier classification}
\label{app:classify}

A verifier is \emph{working} if it (a)~accepts the gold answer $a$, (b)~rejects each of the four adversarial wrong candidates $\{a-1, a+1, a+7, 42\}$, (c)~halts within 10\,s, and (d)~raises no unhandled exception. A verifier that accepts $a$ but also accepts some adversarial candidate is \emph{trivial-or-broken}. A verifier that fails to accept $a$ is \emph{wrong-spec}.

%------------------------------------------------------------------------------
\section{Statistical Methodology and Pre-registration}
\label{app:stats}
%------------------------------------------------------------------------------

\textbf{Confidence intervals.} 95\% Clopper-Pearson exact binomial intervals via SciPy 1.13's \texttt{binomtest(\,).proportion\_ci(method="exact")}. Bootstrap AUROC intervals use $1{,}000$ resamples drawn with replacement.

\textbf{Hypothesis tests.} Matched-binary comparisons use McNemar's exact mid-$p$ test via \texttt{statsmodels.stats.contingency\_tables.mcnemar(exact=True)}~\citep{fagerland2013mcnemar}. The 2$\times$2 ablation uses Fisher's exact test on the contingency table $(44, 0; 276, 334)$, yielding $p<10^{-8}$.

\textbf{Pre-registration text} (committed before the $n{=}498$ scale-up):
\begin{quote}\itshape\small
Hypothesis: strict two-way consensus (Llama $\cap$ DeepSeek-V3) achieves top-tier precision $\geq 99\%$ on the full MATH-500. Branches: (A) precision $\geq 99\%$, claim publishable; (B) $95\%\leq$ precision $<99\%$, report exact number, no overclaim; (C) precision $<95\%$, audit each false acceptance, report ablations; halt-and-audit if precision $<90\%$. Locked parameters: adversarial probe set $\{\hat a\pm 1, \hat a+7, \hat a\times 2\}$ (integer fallback $\{0,1,-1,42,100\}\setminus\{\hat a\}$); 10\,s sandbox timeout; working-verifier definition per \Cref{app:classify}.
\end{quote}
The realized result was $171/171 = 1.000$, $[0.979, 1.000]$, fulfilling Branch A.

%------------------------------------------------------------------------------
\section{Extended Results}
\label{app:results}
%------------------------------------------------------------------------------

\subsection{Same-model FAR by difficulty (Table~\ref{tab:far})}

\begin{table}[h]
\centering
\caption{\textbf{Same-model SymPy false acceptance rate on MATH-500 by difficulty.} Solver and verifier are both Qwen2.5-Math-7B-Instruct. $n$ = number of \textsc{AllPass} verdicts at each level. Total \textsc{AllPass}: $n=320$.}
\label{tab:far}
\small
\begin{tabular}{lcccccc}
\toprule
Level & L1 & L2 & L3 & L4 & L5 & Overall \\
\midrule
FAR   & 1.4\% & 7.7\% & 13.1\% & 17.2\% & 30.8\% & 13.8\% \\
$n$   & 71    & 65    & 61     & 58     & 65     & 320 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{2$\times$2 ablation: independence is the operative axis}

A 2$\times$2 design crossed independence (solution- vs.\ specification-grounded extraction) with randomization (random evaluation points vs.\ deterministic symbolic checks). Both spec-grounded cells produced 0 false accepts ($0/165$, $0/169$); both solution-grounded cells produced FAR $\approx 13.8\%$. Fisher's exact on the contingency table $(44, 0; 276, 334)$ yields $p<10^{-8}$ in favor of the independence axis.

\subsection{Agreement/entropy signal collapse on contamination-clean benchmarks (Table~\ref{tab:contam})}

\begin{table}[h]
\centering
\caption{\textbf{Selective-prediction signals on contamination-assisted MATH-500 vs.\ contamination-clean AIME 2025 and CleanMath.} ``--'' = empty top tier. Solver: Qwen2.5-7B-Instruct-Turbo.}
\label{tab:contam}
\small
\begin{tabular}{lrrr}
\toprule
Method & MATH-500 & AIME 2025 & CleanMath \\
\midrule
Verbalized            & 131/166 & 3/16    & 4/12  \\
Self-Consistency 4/4  & 105/118 & ---     & ---   \\
Template SGRV         & 59/59   & ---     & ---   \\
ExeVer same-model     & 276/320 & ---     & ---   \\
SE SymPy (zero-ent)   & 101/112 & ---     & 1/6   \\
SE NLI (zero-ent)     & 114/131 & 1/16    & 5/59  \\
$p(\textsc{True})$ AUROC & 0.562 & 0.463 & 0.474 \\
\bottomrule
\end{tabular}
\end{table}

On AIME 2025 the solver is uniformly uncertain ($\geq 8$ distinct samples on nearly every problem), so the 4/4 self-consistency tier is empty. On CleanMath the solver is uniformly and confidently wrong (12\% accuracy), and the NLI variant of semantic entropy collapses paraphrases of the same wrong answer into a single confident-looking cluster (5/59 correct).

\subsection{Per-extractor verifier classification on MATH-175 (Table~\ref{tab:perext-app})}

\begin{table}[h]
\centering
\caption{\textbf{Per-extractor verifier classes on MATH-175.} ``Trivial-or-broken'' equals the headline rate at which the deployment-time filter intervenes. Total $n{=}175$ per row.}
\label{tab:perext-app}
\small
\begin{tabular}{lrrrr}
\toprule
Extractor & Working & Wrong-spec & Trivial-or-broken & \textsc{Unverif.} \\
\midrule
Llama-3.3-70B          & 119 & 21 & 13 & 22 \\
DeepSeek-V3            & 124 & 18 & 11 & 22 \\
Claude Sonnet 4.6      & 112 & 23 & 18 & 22 \\
gpt-oss-120b           &  98 & 30 & 24 & 23 \\
Qwen3-Coder-480B       & 105 & 27 & 19 & 24 \\
GPT-5-mini             & 102 & 29 & 21 & 23 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Lab-agnostic five-way consensus}

Adding extractors monotonically shrinks the accepted tier on stratified MATH-175 while preserving precision: $73$ (Llama) $\to 72$ (Llama $\cap$ DeepSeek) $\to 69$ (3-way) $\to 69$ (4-way) $\to 69$ (5-way) $\to 67$ (6-way with GPT-5-mini), all at precision $1.000$.

\subsection{Putnam scope test}

On a $100$-problem random sample of PutnamBench, the proof-mode prompt permits explicit \texttt{UNVERIFIABLE} refusals. Refusal rates: Claude Sonnet 4.6 $51/100$, GPT-5-mini $35/100$, DeepSeek-V3 $44/100$, Llama-3.3-70B $39/100$. Among non-refused problems, working-verifier-and-gold-accepted: Claude $19/49$, GPT-5-mini $8/65$, DeepSeek $14/56$, Llama $11/61$.

\subsection{Lean compile-rate audit}

A pilot Lean~4 hybrid was implemented for $200$ MATH-500 problems by prompting Claude Sonnet 4.6 to emit, alongside the SymPy verifier, a Lean~4 theorem statement of the form \texttt{theorem problem : <constraint>} with placeholder \texttt{by sorry}. Compile rate against Mathlib4 $4.10.0$ was $158/200 = 78.9\%$; failures were predominantly import resolution and unicode-symbol parsing, not type-mismatch errors. This rate motivates the hybrid SymPy-plus-Lean follow-up; it is not used in any X-SGRV result.

%------------------------------------------------------------------------------
\section{Verifier Case Studies}
\label{app:cases}
%------------------------------------------------------------------------------

\subsection{Working compound verifier (MATH-500, Level 4 algebra)}

Problem (paraphrased): \emph{Find the product of all real roots of $x^2 - 5x + 6 = 0$.}

\begin{lstlisting}[style=xsgrv]
def verify(answer):
    try:
        x = sympy.symbols('x')
        roots = sympy.solve(x**2 - 5*x + 6, x)
        product = sympy.prod(roots)
        return sympy.simplify(sympy.sympify(answer) - product) == 0
    except Exception:
        return False
\end{lstlisting}

\subsection{Working enumeration verifier (CleanMath/HMMT-Feb 2025)}

\begin{lstlisting}[style=xsgrv]
def verify(answer):
    try:
        n = int(str(answer).strip())
        count = 0
        for a in range(1, 10):
            for b in range(0, 10):
                for c in range(0, 10):
                    if (a + b + c) == 12 and a*b*c % 7 == 0:
                        count += 1
        return n == count
    except Exception:
        return False
\end{lstlisting}

\subsection{Broken verifier rejected by the deployment-time filter}

The following script accepts the gold answer but also accepts $\hat a + 7$ and is rejected by the deployment-time filter:

\begin{lstlisting}[style=xsgrv]
def verify(answer):
    try:
        return int(str(answer).strip()) % 7 == 0
    except Exception:
        return False
\end{lstlisting}

%------------------------------------------------------------------------------
\section{Limitations and Broader Impact}
\label{app:impact}
%------------------------------------------------------------------------------

\textbf{Operational scope.} X-SGRV is a structurally-grounded selective-prediction signal, not a continuous-score uncertainty estimator. Top-tier coverage is single-digit on contamination-clean competition mathematics by design, because structural verifiability of a competition problem is a property of the problem, not of solver confidence. On Omni-MATH hard-100 (difficulty $9.0$--$9.5$) zero working verifiers are produced, defining the operational ceiling on non-proof problems. On PutnamBench-style proof problems the system self-detects scope by emitting \texttt{UNVERIFIABLE} on roughly half of a 100-problem sample.

\textbf{Reliance on a strong cross-family extractor.} The empirical results require a $\geq 70$B cross-family extractor; at the $7$B scale the working-verifier rate on MATH-500 is below $15\%$. The asymmetric extractor/solver pairing is consistent with centralized-governance safety patterns~\citep{ste2024,xiong2024llmuncertainty} but is a deployment cost.

\textbf{Independence assumption.} The consensus argument relies on an independence assumption between extractor families. The empirical $0/171$ at the $n{=}498$ scale places a lower bound on effective independence but is not a structural proof. The proposed falsification protocol --- empirical pairwise correlation between extractor verifier outputs vs.\ the independence-bound prediction --- is described as future work in the discussion.

\textbf{Broader impact.} X-SGRV supports \emph{abstention} on uncertain mathematical reasoning, not substitute for human review. Deploying it in high-stakes settings (automated grading, safety-critical scientific computation, medical decision support) without an explicit human-in-the-loop fallback would invert the safety pattern the system is designed to support: the right deployment posture is to escalate, not commit, when the verifier abstains. Top-tier acceptances on contamination-clean benchmarks (e.g., $4/4$ on CleanMath) are correct in our experiments, but a deployment policy that treats individual accepts as authoritative without human review would be misuse.

\textbf{Energy and compute footprint.} The full $n{=}498$ MATH-500 scale-up consumed approximately $3.1\times 10^6$ output tokens across all extractor and solver calls, equivalent to roughly $\$45$ in API costs at 2026-04 list prices. PRM baselines required approximately $4$ A100-hours on Modal. No model fine-tuning was performed.

\end{document}
